---
name: Stephanie Tring
title: "HW4"
output: github_document

---


## Part 1: HPC

# Problem 1: Make sure your code is nice
Rewrite the following R functions to make them faster. It is OK (and recommended) to take a look at Stackoverflow and Google
The following functions can be written to be more efficient without using
parallel:



```{r p1-fun1, eval = TRUE}

# Total row sums
fun1 <- function(mat) {
  n <- nrow(mat)
  ans <- double(n) 
  for (i in 1:n) {
    ans[i] <- sum(mat[i, ])
  }
  ans
}

fun1alt <- function(mat) {
 
 #cbind(ans, total=rowSums(ans))
  
  ans <- rowSums(mat)
  ans

}

 x1 <- matrix(rnorm(1000000),nrow=100)
# Benchmarking
microbenchmark::microbenchmark(
  fun1(x1),
  fun1alt(x1), unit='relative'
)




```

```{r p2-fun2}
# Cumulative sum by row
fun2 <- function(mat) {
  n <- nrow(mat)
  k <- ncol(mat)
  ans <- mat
  for (i in 1:n) {
    for (j in 2:k) {
      ans[i,j] <- mat[i, j] + ans[i, j - 1]
    }
  }
  ans
}

fun2alt <- function(mat) {
  n <- nrow(mat)
  ans <- mat
  for (i in 1:n) {
    ans[i,] <- cumsum(mat[i,])
  }
  ans
}

 x2 <- matrix(rnorm(10000),nrow=100)

# Benchmarking
microbenchmark::microbenchmark(
  fun2(x2),
  fun2alt(x2), unit='relative'
)


```

```{r dat}
# Use the data with this code
set.seed(2315)
dat <- matrix(rnorm(200 * 100), nrow = 200)



# Test for the first
microbenchmark::microbenchmark(
  fun1(dat),
  fun1alt(dat), unit = "relative", check = "equivalent"
)

# Test for the second
microbenchmark::microbenchmark(
  fun2(dat),
  fun2alt(dat), unit = "relative", check = "equivalent"
)


```





# Problem 2: Parallelize everyhing



```{r sim_pi}
sim_pi <- function(n = 1000, i = NULL) {
  p <- matrix(runif(n*2), ncol = 2)
  mean(rowSums(p^2) < 1) * 4
}

# Here is an example of the run
set.seed(156)
sim_pi(1000) # 3.132

#In order to get accurate estimates, we can run this function multiple times, with the following code:

# This runs the simulation a 4,000 times, each with 10,000 points
set.seed(1231)
system.time({
  ans <- unlist(lapply(1:4000, sim_pi, n = 10000))
  print(mean(ans))
})


```





```{r parallel}
library(parallel)

 
  # Making the cluster using `ncpus`
  # STEP 1: Make cluster
 system.time ({  
 cl <- parallel::makePSOCKcluster(4)

  # STEP 2: Set it up (espoty if needed, idx and dat)
  
 clusterSetRNGStream(cl, 1231)

  
    # STEP 3: THIS FUNCTION NEEDS TO BE REPLACES WITH parLapply
ans <- unlist(parLapply(cl, 1:4000, sim_pi, n=10000))
   print(mean(ans))
  
  # STEP 4: Gsopt the cluster
  parallel::stopCluster(cl)
  ans
  
})




```

## SQL


```{r}
# install.packages(c("RSQLite", "DBI"))

library(RSQLite)
library(DBI)

# Initialize a temporary in memory database
con <- dbConnect(SQLite(), ":memory:")

# Download tables
film <- read.csv("https://raw.githubusercontent.com/ivanceras/sakila/master/csv-sakila-db/film.csv")
film_category <- read.csv("https://raw.githubusercontent.com/ivanceras/sakila/master/csv-sakila-db/film_category.csv")
category <- read.csv("https://raw.githubusercontent.com/ivanceras/sakila/master/csv-sakila-db/category.csv")

# Copy data.frames to database
dbWriteTable(con, "film", film)
dbWriteTable(con, "film_category", film_category)
dbWriteTable(con, "category", category)

dbListTables(con)


```


```{sql connection=con}
PRAGMA table_inf(film_category)
```



```

When you write a new chunk, remember to replace the r with sql, connection=con. Some of these questions will reqruire you to use an inner join. Read more about them here https://www.w3schools.com/sql/sql_join_inner.asp

# Question 1
How many many movies is there avaliable in each rating catagory.
```{sql, connection=con}

```





```{sql, connection=con}
select rating, count(film_id) as movies
from film
group by rating

```

# Question 2
What is the average replacement cost and rental rate for each rating category.
```{sql connection=con}
select rating, avg(replacement_cost) as average_replacement_cost, avg(rental_rate) as average_rental_rate
from film
group by rating


```

# Question 3
Use table film_category together with film to find the how many films there are witth each category ID

```{sql connection=con}

select category_id, count(a.film_id) as film
from film_category a join film b
on a.film_id=b.film_id
group by category_id


```

# Question 4
Incorporate table category into the answer to the previous question to find the name of the most popular category.
```{sql connection=con}
select category_id, count(a.film_id) as film
from film_category a join film b 
on a.film_id=b.film_id
join category c on a.category_ud=c.category_id
group by a.category_id
order by films desc


```

