---
name: Stephanie Tring
title: "Assignment 03 - Web Scraping and Text Mining"
output: html_document
output2: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### API

## API_1

-Using the NCBI API, look for papers that show up under the term "sars-cov-2 trial vaccine." Look for the data in the pubmed database, and then retrieve the details of the paper as shown in lab 7. How many papers were you able to find?

- Using the NCBI API for "sars-cov-2 trial vaccine," I retrieved 564 papers.

```{r counter-pubmed, eval=TRUE}
library(xml2)
# Downloading the website
website <- xml2::read_html("https://pubmed.ncbi.nlm.nih.gov/?term=sars-cov-2+trial+vaccine")
# Finding the counts
counts <- xml2::xml_find_first(website, '/html/body/main/div[9]/div[2]/div[2]/div[1]')
# Turning it into text
counts <- as.character(counts)
# Extracting the data using regex
stringr::str_extract(counts, "[0-9,]+")
```

## API_2

-Using the list of pubmed ids you retrieved, download each papers’ details using the query parameter rettype = abstract. If you get more than 250 ids, just keep the first 250.

```{r query pubmed, eval=TRUE}
library(httr)
query_ids <- GET(
  url   = "https://eutils.ncbi.nlm.nih.gov/entrez/eutils/esearch.fcgi",
  query = list(
    db     = "pubmed",
    term   = "sars-cov-2 trail vaccine",
    retmax = 250
  )
)
# Extracting the content of the response of GET
ids <- httr::content(query_ids)
```

-There are 3 publication with the query term "sars-cov-2 trail vaccine"

```{r return IDS}
library (stringr)
# Turn the result into a character vector
ids <- as.character(ids)
list(ids)
# Find all the ids 
ids <- stringr::str_extract_all(ids, "<Id>[0-9]+</Id>")[[1]]
# Remove all the leading and trailing <Id> </Id>. Make use of "|"
ids <- stringr::str_remove_all(ids, "PATTERN")
```



```{r get-abstracts, eval = TRUE}

publications <- GET(
  url   = "https://eutils.ncbi.nlm.nih.gov/entrez/eutils/efetch.fcgi",
  query = list(
    db= "pubmed",
    id= paste (ids, collapse= ","),
    retmax= 250,
    rettype= "abstract"
    )
)
# Turning the output into character vector
publications <- httr::content(publications)
publications_txt <- as.character(publications)
#list(publications_txt)
```


```{r}
pub_char_list <- xml2::xml_children(publications)
pub_char_list <- sapply(pub_char_list, as.character)

```



```{r}
library(stringi)
abstracts <- str_extract(pub_char_list, "<Abstract>(\\n|.)+</AbstractText>")
abstracts<- str_remove_all(abstracts, "</?[[:alnum:]]+>")
abstracts <- str_replace_all(abstracts, "\\s+", " ")
table(is.na(abstracts))
```

```{r Titles}
titles <- str_extract(pub_char_list[1], "<ArticleTitle>(\\n|.)+</ArticleTitle>")
titles<- str_remove_all(titles, "</?[[:alnum:]]+>")
```

```{r Name of Journal}
journal <- str_extract(pub_char_list[1], "</JournalIssue>(\\n|.)+</Title>")
journal<- str_remove_all(journal, "</?[[:alnum:]]+>")
```

```{r Publication date}
pubdate <- str_extract(pub_char_list[1], "<PubDate>(\\n|.)+</PubDate>")
pubdate<- str_remove_all(pubdate, "</?[[:alnum:]]+>")

```





```{r}
database <- data.frame(
  PubMedID= ids,
  NameOfJournal= journal,
  PublicationDate= pubdate,
  Title= titles,
  Abstracts= abstracts
)
knitr::kable(database)
```

### Text Miniing

## Test_mining_1

```{r read in dataset }
# Read in dataset
library (data.table)

library(leaflet)
library(tidyverse)
library(lubridate)
library(tidytext)
library(ggplot2)


download.file("https://raw.githubusercontent.com/USCbiostats/data-science-data/master/03_pubmed/pubmed.csv", "pubmed.csv", method="libcurl", timeout = 60)
pubmed <- data.table::fread("pubmed.csv")


```

```{r}
head(pubmed)
```

```{r}
pubmed %>% 
  unnest_tokens(output = token, input = abstract) %>%
  count(token, sort = TRUE) %>%
  top_n(10, n) %>%
  ggplot(aes(x=n, y=(fct_reorder(token, n)))) +
  geom_col()
```
- In the initial tokenize, I see that stop words overtook the top 5 of most appeared. With "the" and "of" appearing the most and "covid," "19" and "is" at the bottom of the top 10. The interesting part is that the word "covid" and "19" do not always appear together, "covid" appear slightly more than "19."


```{r removing stopwords}
library(stringr)
library(forcats)
number_words<-as.character(seq(0,100))

pubmed %>%
  unnest_tokens(output= word,input= abstract) %>%
  anti_join(tidytext :: stop_words, by="word") %>%
  filter (!(word %in% number_words)) %>%
  count( word, sort = TRUE) %>%
  top_n(20, n) %>%
  ggplot(aes(n, fct_reorder(word, n))) +
  geom_col()
```

- After removing the 19,987 stopwords, I see that "covid" is the top appeared word, however it also took "19" as a stop word and removed it as well. The top 5 token after removing stopwords are "covid," "patients," "cancer," "preclampsia," and "fibrosis"


```{r top 5 per term}
number_words<-as.character(seq(0,100))

pubmed %>%
  unnest_tokens(output= word,input= abstract) %>%
  anti_join(tidytext :: stop_words, by="word") %>%
  filter (!(word %in% number_words)) %>%
  group_by(term) %>%
  count( word, sort = TRUE) %>%
  top_n(5, n) %>%
  ggplot(aes(n, fct_reorder(word, n))) +
  geom_col()

```
 
- The top five sorted in the terms are "covid," "cancer," "prostate," and "eclampsia."


## Text_mining_2

```{r bi-grams and ggplot}
pubmed %>% 
  unnest_ngrams(output = ngram, input = abstract, n=2) %>%
  count(ngram, sort = TRUE) %>%
  top_n(20, n) %>%
  ggplot(aes(x=n, y=(fct_reorder(ngram, n)))) +
  geom_col()
```
- Of the top 10 bigram, "covid" and "19" appear the most together at nearly 7000 times and 2500 more times than the next most common which is "of" and "the."

## Text_mining_3


```{r}
pubmed %>%
  unnest_tokens(document, abstract) %>%
  count(document,term) %>%
  bind_tf_idf(document, term, n) %>%
  group_by(term) %>%
  arrange(desc(tf_idf))
```
- Based off thr TF-IDF calculations:
[covid] covid, coronavirus, pandemic, sars and cov
[prostate cancer] prostate cancer, androgen, psa, prostatectomy, and castration
[preclampsia] ecalampsia, preeclampsia, pregnancy, maternal, and gestational
[meningitis] meningitis, meningeal, pachymeningitis, csf and meninges
[cystic fibrosis]cf, fibrosis, cystis, cftr, and sweat

The results are different in that in the TF, we see that number of tokens connected in the document and in the method used in Q1 we see the overall count. 
